---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# dpp
dplyr for paired calculations

dpp depends on dplyr and imports proj4, and can be installed with 

```{r,eval=FALSE,message=FALSE}
devtools::install_github("mdsumner/dpp")
```

In the function `simd` I apply a geographic transformation on two columns x,y in a `tbl_df`. To do this I extract the columns as a matrix and pass them to proj4::project, then pull them back to copy over the original longitude/latitude x,y columns. 

The function is used like this: 

```{r,echo=TRUE,message=FALSE}
library(dpp) 
x <- simd(n = 10, p = "+proj=laea")
```
and it works like this: 

```{r,eval=FALSE,echo=TRUE,message=FALSE}
  x <- data_frame(x = runif(n, -180, 180), y = runif(n, -90, 90), id = seq(n))
  if (!is.null(p)) {
    m <- as.matrix(x[,c("x", "y")])
    m <- project(m, p)
    x$x <- m[,1L]
    x$y <- m[,2L]
  }
```
The question: is there a more dplyr-ish way to apply this paired variable mutation, without extracting to the matrix? Ultimately I'd like to have project methods for objects composed of tbl_dfs, so perhaps I need to write a new version of proj4::project that works more deeply with dplyr?
